---
title: "project 5"
author: "Chengcen Zhou"
date: "4/26/2017"
output: html_document
runtime: shiny
---

```{r}

require(readxl)
require(hashmap)
require(ggmap)
require(ggrepel)
require(dplyr)
require(ggplot2)
#Clean Data

#Empty data frame
h1b_df = data.frame()

h1b=read.csv("/Users/Connie/Desktop/Spr2017-proj5-grp7/data/h1b_kaggle.csv")


index1=which(h1b$CASE_STATUS=="CERTIFIED")
index2=which(h1b$CASE_STATUS=="DENIED")
index3=which(h1b$CASE_STATUS=="CERTIFIED-WITHDRAWN")
index4=which(h1b$CASE_STATUS=="WITHDRAWN")
index=c(index1,index2,index3,index4)
h1b=h1b[index,]


h1b=h1b[!is.na(h1b$lon),]
h1b=h1b[!is.na(h1b$lat),]

h1b$SOC_NAME=as.factor(toupper(h1b$SOC_NAME))
h1b[which(h1b$SOC_NAME=="COMPUTER OCCUPATIONS, ALL OTHER*"),"SOC_NAME"]="COMPUTER OCCUPATIONS, ALL OTHER"
h1b[which(h1b$SOC_NAME=="NETWORK AND COMPUTER SYSTEMS ADMINISTRATORS*"),"SOC_NAME"]="NETWORK AND COMPUTER SYSTEMS ADMINISTRATORS"

h1b$WORKSITE<-as.character(h1b$WORKSITE)
citystate <-data.frame(matrix(unlist(strsplit(h1b$WORKSITE,", ")),ncol = 2,byrow = T))
colnames(citystate)=c("WORKSITE_CITY","WORKSITE_STATE")
h1b=cbind(h1b,citystate)
 
names(h1b)

#Changing column names of data for matching
#print("Column matching ..")

print("Column matching ..")
{
   h1b= h1b %>%
             mutate(X = CASE_NUMBER,
                    #CASE_STATUS = CASE_STATUS,
                    #EMPLOYER_NAME = EMPLOYER_NAME,
                    #SOC_NAME = SOC_NAME,
                    #JOB_TITLE = JOB_TITLE,
                    #FULL_TIME_POSITION = FULL_TIME_POSITION,
                    #PREVAILING_WAGE = PREVAILING_WAGE,
                    WORKSITE_CITY = CITY,
                    WORKSITE_STATE = STATE)
}

# Adding Year column to dataframe
  print("Mutating year ..")
  h1b = h1b %>%
    mutate(YEAR = as.character(YEAR))

  print(paste0("Mutated data size: ", as.character(dim(h1b_df))))  

# Selecting only the relevant columns
  h1b = h1b %>%
             select(CASE_NUMBER,
                    CASE_STATUS,
                    EMPLOYER_NAME,
                    SOC_NAME,
                    JOB_TITLE,
                    FULL_TIME_POSITION,
                    PREVAILING_WAGE,
                    WORKSITE_CITY,
                    WORKSITE_STATE,
                    YEAR)

  
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r}


#Full time position distribution
h1b %>%
  group_by(FULL_TIME_POSITION) %>%
  summarise(count = n(),percentage = 100*count/(dim(h1b)[1]))
#For filling the missing values,  then analyze the relationship of the Prevailing Wage with Full Time Position across the years.
# Generic ggplot graphics configuration I will be using for all my plots
get_theme <- function() {
  return(theme(axis.title = element_text(size = rel(1.5)),
          legend.position = "bottom",
          legend.text = element_text(size = rel(1.5)),
          legend.title = element_text(size=rel(1.5)),
          axis.text = element_text(size=rel(1.5))))
}

# Avoid scientific notation in plot
options(scipen = 999)

g <- ggplot(data = h1b, aes(x=YEAR, y = PREVAILING_WAGE))
g <- g + geom_boxplot(aes(fill=FULL_TIME_POSITION)) + coord_cartesian(ylim=c(0,125000))
g <- g + xlab("YEAR") + ylab("WAGE (USD)") + get_theme()
g




```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
h1b_df = data.frame()
print("Column matching ..")
{
   h1b= h1b %>%
             mutate(CASE_NUMBER = X,
                    #CASE_STATUS = CASE_STATUS,
                    #EMPLOYER_NAME = EMPLOYER_NAME,
                    #SOC_NAME = SOC_NAME,
                    #JOB_TITLE = JOB_TITLE,
                    #FULL_TIME_POSITION = FULL_TIME_POSITION,
                    #PREVAILING_WAGE = PREVAILING_WAGE,
                    WORKSITE_CITY = CITY,
                    WORKSITE_STATE = STATE)
}

# Adding Year column to dataframe
  print("Mutating year ..")
  h1b = h1b %>%
    mutate(YEAR = as.character(YEAR))

  print(paste0("Mutated data size: ", as.character(dim(h1b_df))))  

# Selecting only the relevant columns
  h1b = h1b %>%
             select(CASE_NUMBER,
                    CASE_STATUS,
                    EMPLOYER_NAME,
                    SOC_NAME,
                    JOB_TITLE,
                    FULL_TIME_POSITION,
                    PREVAILING_WAGE,
                    WORKSITE_CITY,
                    WORKSITE_STATE,
                    YEAR)

#Full time position distribution
h1b %>%
  group_by(FULL_TIME_POSITION) %>%
  summarise(count = n(),percentage = 100*count/(dim(h1b)[1]))
#For filling the missing values,  then analyze the relationship of the Prevailing Wage with Full Time Position across the years.
# Generic ggplot graphics configuration I will be using for all my plots
get_theme <- function() {
  return(theme(axis.title = element_text(size = rel(1.5)),
          legend.position = "bottom",
          legend.text = element_text(size = rel(1.5)),
          legend.title = element_text(size=rel(1.5)),
          axis.text = element_text(size=rel(1.5))))
}

# Avoid scientific notation in plot
options(scipen = 999)

g <- ggplot(data = h1b, aes(x=YEAR, y = PREVAILING_WAGE))
g <- g + geom_boxplot(aes(fill=FULL_TIME_POSITION)) + coord_cartesian(ylim=c(0,125000))
g <- g + xlab("YEAR") + ylab("WAGE (USD)") + get_theme()

g
  
```

```{r}
state_abbs = c("AK", "AL", "AR", "AZ", "CA", "CO", "CT", "DC", "DE", "FL", "GA",
                                         "HI", "IA", "ID", "IL", "IN", "KS", "KY", "LA", "MA", "MD", "ME",
                                         "MI", "MN", "MO", "MS",  "MT", "NC", "ND", "NE", "NH", "NJ", "NM",
                                         "NV", "NY", "OH", "OK", "OR", "PA", "PR", "RI", "SC", "SD", "TN",
                                         "TX", "UT", "VA", "VT", "WA", "WI", "WV", "WY")

state_full = c("alaska","alabama","arkansas","arizona","california","colorado",
                                       "connecticut","district of columbia","delaware","florida","georgia",
                                       "hawaii","iowa","idaho","illinois","indiana","kansas","kentucky",
                                       "louisiana","massachusetts","maryland","maine","michigan","minnesota",
                                       "missouri","mississippi","montana","north carolina","north dakota",
                                       "nebraska","new hampshire","new jersey","new mexico","nevada",
                                       "new york","ohio","oklahoma","oregon","pennsylvania","puerto rico",
                                       "rhode island","south carolina","south dakota","tennessee","texas",
                                       "utah","virginia","vermont","washington","wisconsin",
                                       "west virginia","wyoming")
 
state_hash = hashmap(state_abbs,state_full)
h1b$WORKSITE_STATE_FULL = sapply(h1b$WORKSITE_STATE, function(x,y) {return(toupper(y[[x]]))}, y = state_hash)
```

```{r}
site_merge <- function(x,y) {
  return(paste0(x,", ",y))
}

h1b %>%
  rename(WORKSITE_STATE_ABB = WORKSITE_STATE) -> h1b

h1b$WORKSITE = mapply(site_merge,h1b$WORKSITE_CITY,h1b$WORKSITE_STATE_FULL)
wrong_names = c("NEW YROK, NEW YORK", "SUUNYVALE, CALIFORNIA", "SAN FRANSISCO, CALIFORNIA")

h1b %>% 
  filter(WORKSITE %in% wrong_names) %>%
  group_by(WORKSITE) %>%
  summarise(count = n())
h1b %>% 
  group_by(WORKSITE) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) -> sites_count

site_hash = hashmap(sites_count$WORKSITE, sites_count$count)
```

```{r}
get_inserts <- function(split_left,split_right, i, letters) {
  # Generate insertions of a single letter
  return(unlist(sapply(letters, function(left,right,c) {return(paste0(left, c, right))}, left = split_left[i], right = split_right[i])))
}

get_deletes <- function(split_left,split_right, i) {
  # Generate deletion of one letter from word
  return(paste0(split_left[i], substr(split_right[i],2,nchar(split_right[i]))))
}

get_replaces <- function(split_left,split_right, i,letters) {
  # Generate replacement of a letter by a-z or space
  if(!is.null(split_right[i]) &  nchar(split_right[i]) > 0) {
      return(unlist(sapply(letters, function(left,right,c) {return(paste0(left, c, right))}, left = split_left[i], right = substr(split_right[i],2,nchar(split_right[i])))))
  }
  return(NULL)
}

get_transposes <- function(split_left, split_right,i) {
  # Generate interchanging of the positions of adjacent letters
  if(!is.null(split_right[i]) & nchar(split_right[i]) > 1) {
    return(paste0(split_left[i],substr(split_right[i],2,2),substr(split_right[i],1,1),substr(split_right[i],3,nchar(split_right[i]))))
  }
  return(NULL)
}

edits1site <- function(site) {
  # All edits that are one edit away from site
  letters = toupper(strsplit("abcdefghijklmnopqrstuvwxyz ",split='')[[1]])
  site_len <- nchar(site)
  #print(site_len)
  if(site_len < 4) {
    return(site)
  }
  split_left <- sapply(seq(0,site_len), substr,x = site,start = 1)
  split_right <- sapply(seq(1,site_len+1), substr,x = site,stop = site_len) 
  deletes <- sapply(seq(1,site_len+1),get_deletes, split_left = split_left, split_right = split_right)
  transposes <- unlist(sapply(seq(1,site_len+1),get_transposes, split_left = split_left, split_right = split_right))
  replaces <- unlist(sapply(seq(1,site_len+1),get_replaces, split_left = split_left, split_right = split_right, letters=letters))
  inserts <- unlist(sapply(seq(1,site_len+1),get_inserts, split_left = split_left, split_right = split_right,letters = letters))
  
  return(unique(c(deletes,transposes,replaces,inserts)))
}

edits2site <- function(site) { 
    # All edits that are two edits away from `word`
    edits1_sites = edits1site(site)
    return (unlist(sapply(edits1_sites, edits1site)))
}

get_prob <- function(site, site_hash) {
  # probability of site in our dataset
  return(site_hash[[site]])
}

known <- function(sites,site_hash = site_hash) {
  # The subset of candidate sites that appear in the dictionary of sites
  return(sites[site_hash$has_keys(sites)])
}

find_candidates <- function(site,...) {
  # Generate possible spelling corrections for word
  return(c(known(site,...), known(edits1site(site),...), c(site)))
}

site_spell_correcter <- function(site,...) {
  # best possible correction to the site
  candidates = find_candidates(site,...)
  best_candi = candidates[which.max(sapply(candidates,get_prob, ...))]
  
  #if(get_prob(best_candi,...) > get_prob(site,...) ) {
  #  return(best_candi)
  #}
  return(best_candi)
}

site_count <- function(site, site_hash) {
  
  if(site_hash$has_key(site)) {
    return(site_hash[[site]])
  }
  return(site)
}
```

```{r}
sites <- sites_count$WORKSITE
sites_before <- c()
sites_after <- c()
count <- 0

for(site in sites) {
  # Count of current Worksite
  curr_count <- site_count(site,site_hash)
  #print(paste0(site, ", ",curr_count))
  
  if(curr_count < 100) { # Threshold
    #print(paste0(site, ", ",curr_count))
    corrected <- site_spell_correcter(site,site_hash)
    
    if(corrected != site) { # Correction occurred
      count <- count + 1
      sites_before[count] <- site
      sites_after[count] <- corrected
      corrected_count <- site_count(corrected,site_hash)
      #print(paste0(site, " : ", curr_count,", ",corrected, " : ", corrected_count))
    }
  }  
}

sites_corrected_hash <- hashmap(sites_before,sites_after)
if(hash$has_key(x)) {
    return(hash[[x]])
  }
  return(x)


h1b$WORKSITE_CORRECTED <- sapply(h1b$WORKSITE,worksite_correct,hash=sites_corrected_hash)
h1b %>%
  select(-WORKSITE) %>%
  rename(WORKSITE = WORKSITE_CORRECTED) -> h1b
```

```{r}

library(ggmap)

top_sites <- (sites_count$WORKSITE)[1:2500]

site_geocodes <- cbind(geocode(top_sites),top_sites)
site_geocodes %>%
  rename(WORKSITE = top_sites) -> site_geocodes

saveRDS(site_geocodes,"geocodes.RDS")
N_sites_geocoded <- dim(site_geocodes)[1]

share <- 100*sum((sites_count$count)[1:N_sites_geocoded])/(dim(h1b)[1])

print(paste0("Records captured by geocoded sites: ", share))
h1b <- full_join(h1b,site_geocodes,by="WORKSITE")

head(h1b)
```

```{r}

###### helper.r #####
job_filter <- function(df,input_vec) {
 
  # If input_vec is empty, return without any filtering
  if(length(input_vec) == 0) {
    return(df %>%
             mutate(JOB_INPUT_CLASS = JOB_TITLE))
  }
  
  new_df <- data.frame()
  
  for(value in input_vec){
    new_df <- rbind(new_df, df %>% 
                      filter(regexpr(value,JOB_TITLE,ignore.case=TRUE) != -1) %>%
                      mutate(JOB_INPUT_CLASS = toupper(value)))
  }
  return(unique(new_df))
}


employer_filter <- function(df, input_vec) {

  if(length(input_vec) == 0) {
    return(df)
  }
  
  new_df <- data.frame()
  
  for(value in input_vec){
    new_df <- rbind(new_df, df %>% 
                      filter(regexpr(value,EMPLOYER_NAME,ignore.case=TRUE) != -1))
  }
  return(unique(new_df))
}
  
find_top <- function(df,x_feature,metric, Ntop = 3) {

  arrange_criteria <- interp(~ desc(x), x = as.name(metric))
  
  df %>% 
    group_by_(x_feature) %>% 
    mutate(certified =ifelse(CASE_STATUS == "CERTIFIED",1,0)) %>%
    summarise(TotalApps = n(),
              Wage = median(PREVAILING_WAGE), 
              CertiApps = sum(certified)) %>%
    arrange_(arrange_criteria) -> top_df
  
  top_len <- min(dim(top_df)[1],Ntop)
  
  return(top_df[1:top_len,1])
}

plot_input <- function(df, x_feature, fill_feature, metric,filter = FALSE, ...) {

  #Finding out the top across the entire range independent of the fill_feature e.g. Year
  top_x <- unlist(find_top(df,x_feature,metric, ...))

  
  filter_criteria <- interp(~x %in% y, .values = list(x = as.name(x_feature), y = top_x))
  arrange_criteria <- interp(~ desc(x), x = as.name(metric))

  if(filter == TRUE) {
    df %>%
      filter_(filter_criteria) -> df
  }
  
  #Grouping by not just x_feature but also fill_feature
  return(df %>% 
    group_by_(.dots=c(x_feature,fill_feature)) %>% 
    mutate(certified =ifelse(CASE_STATUS == "CERTIFIED",1,0)) %>%
      summarise(TotalApps = n(),CertiApps = sum(certified), Wage = median(PREVAILING_WAGE)))
}
  
plot_output <- function(df, x_feature,fill_feature,metric, xlabb,ylabb) {  
  
  # Prevents numbers on plot transforming into scientific notation
  options(scipen = 999)
  
  g <- ggplot(df, aes_string(x=x_feature,y=metric)) +
    geom_bar(stat = "identity", aes_string(fill = fill_feature), position = "dodge") + 
    coord_flip() + xlab(xlabb) + ylab(ylabb) + get_theme()
  
  return(g)
}


map_gen <- function(df,metric,USA,...) {

  # Creating Map Dataframe
  df %>%
    mutate(certified =ifelse(CASE_STATUS == "CERTIFIED",1,0)) %>%
    group_by(WORKSITE,lat,lon) %>%
    summarise(TotalApps = n(),CertiApps = sum(certified), Wage = median(PREVAILING_WAGE)) -> map_df
   

  # Finding top Locations for metric
  top_locations <- unlist(find_top(df,"WORKSITE",metric, ...))
  
  # First layer    : USA Map
  # Second layer   : geom_point() with point alpha and size varying with metric
  # Third layer    : points mapping to top locations using ggrepel package
  g <- ggplot(USA, aes(x=long, y=lat)) + 
    geom_polygon() + xlab("Longitude (deg)") + ylab("Latitude(deg)") + 
    geom_point(data=map_df, aes_string(x="lon", y="lat", label = "WORKSITE", alpha = metric, size = metric), color="yellow") + 
    geom_label_repel(data=map_df %>% filter(WORKSITE %in% top_locations),aes_string(x="lon", y="lat",label = "WORKSITE"),
                     fontface = 'bold', color = 'black',
                     box.padding = unit(0.0, "lines"),
                     point.padding = unit(1.0, "lines"),
                     segment.color = 'grey50',
                     force = 3) +
  
    # Using the whole USA map
    coord_map(ylim = c(23,50),xlim=c(-130,-65)) +
    get_theme()
  
  return(g)
}

get_theme <- function() {
  # Function for ggplot2 graphics parameters
  return(
    theme(axis.title = element_text(size = rel(1.5)),
          legend.position = "right",
          legend.text = element_text(size = rel(1.5)),
          legend.title = element_text(size=rel(1.5)),
          axis.text = element_text(size=rel(1.5))) 
  )
}

```


```{r}
###### server.r ####
library(shiny)
library(ggplot2)
library(dplyr)
library(lazyeval)
library(hashmap)
library(ggrepel)
library(maps)
library(stats)
library(rdrop2)
library(mapproj)


#Helper functions
source("helpers.R")

# Initializing value containers used for plotting
metric_lab_hash <- hashmap(c("TotalApps","CertiApps","Wage"),c("TOTAL H-1B VISA APPLICATIONS", "CERTIFIED H-1B VISA APPLICATIONS","MEDIAN PREVAILING WAGE"))
USA = map_data(map = "usa")

# Define Server logic
shinyServer(function(input, output) {
  
  #h1b_df <- readRDS("./data/h1b_shiny.rds")
  
  ## Initializing Reactive values for inputs
  reactive_inputs <- reactiveValues(job_list = c('data scientist','data engineer','machine learning'),
                                    employer_list = c(), 
                                    year = as.character(seq(2011,2016)), 
                                    metric = "TotalApps",
                                    location = "USA",
                                    Ntop = 3)
  
  # Compute button triggers update of reactive inputs
  observeEvent(input$compute,{
    job_list <-tolower(trimws(c(input$job_type_1,input$job_type_2,input$job_type_3)))
    reactive_inputs$job_list <- job_list[job_list != ""]
    
    employer_list <-tolower(trimws(c(input$employer_1,input$employer_2,input$employer_3)))
    reactive_inputs$employer_list <- employer_list[employer_list != ""]
    
    reactive_inputs$year <- as.character(seq(input$year[1], input$year[2]))
    
    reactive_inputs$metric <- input$metric
    
    reactive_inputs$location <- input$location
    
    reactive_inputs$Ntop <- input$Ntop
  })
  
  ## Filtering based on input dimensions: year range, location, job type, employer

  # Filter year input
  year_input <- reactive({
    df %>%
      filter(YEAR %in% reactive_inputs$year)
  })

  # Filter location input
  location_input <- reactive({
    if(reactive_inputs$location == 'USA') year_input() else year_input() %>% filter(WORKSITE_STATE_FULL == reactive_inputs$location)
  })


  # Filtering based on job type
  # If no match found, then use all unique Job Titles
  job_input <- reactive({
    job_filter(location_input(),reactive_inputs$job_list)
  })

  # Filtering based on employer names
  # If no match found, then use all Employers
  employer_input <- reactive({
    #If job types had no match, use the input before job type filtering for employer filtering
    if(dim(job_input())[1] == 0) {
      employer_filter(location_input(),reactive_inputs$employer_list)
    } else {
      employer_filter(job_input(),reactive_inputs$employer_list)
    }
  })

  # Final input data frame for plotting
  data_input <- reactive({
    # If both Job type filter and Employer filter then use only Location and Year filter
    # If job type filter had a match and Employer filter had no match then use up to Job Filter
    # If Employer had match then use up to Employer filter

    if(dim(employer_input())[1] == 0 & dim(job_input())[1] == 0) {
      location_input() %>%
        mutate(JOB_INPUT_CLASS = JOB_TITLE)
    } else if (dim(employer_input())[1] == 0 & dim(job_input())[1] > 0){
      job_input()
    } else if (dim(employer_input())[1] > 0 & dim(job_input())[1] == 0){
      employer_input() %>%
        mutate(JOB_INPUT_CLASS = JOB_TITLE)
    } else {
      employer_input()
    }
  })

  output$dataInput <- renderDataTable({
    head(data_input())
  })

  # output$metricInput <- renderText({
  #   reactive_inputs$metric
  # })

  ## Plotting

  ## Job Type Comparison Plot

  # Job Type Input
  job_plot_input <- reactive({
     plot_input(data_input(),"JOB_INPUT_CLASS", "YEAR",reactive_inputs$metric,filter = TRUE, Ntop = reactive_inputs$Ntop)
   })

  # Job Type data subset
  output$job_type_table <- renderDataTable({
    job_plot_input()
  }, options = list(lengthMenu = c(10, 20,50), pageLength = 10)
  )

  # Job Type Plot
  output$job_type <- renderPlot({
    plot_output(job_plot_input(),"JOB_INPUT_CLASS", "YEAR", reactive_inputs$metric, "JOB TYPE",
                metric_lab_hash[[reactive_inputs$metric]])
  })


  ## Locations Input

  # Location Input
  location_plot_input <- reactive({
    plot_input(data_input(),"WORKSITE", "YEAR",reactive_inputs$metric, filter = TRUE, Ntop = reactive_inputs$Ntop)
  })

  # Location data subset
  output$location_table <- renderDataTable({
    location_plot_input()
  }, options = list(lengthMenu = c(10, 20,50), pageLength = 10)
  )

  # Locations Plot
  output$location <- renderPlot({
    plot_output(location_plot_input(),"WORKSITE", "YEAR", reactive_inputs$metric,"LOCATION",
                metric_lab_hash[[reactive_inputs$metric]])
  })

   ## Employers Input

   # Employers input
   employer_plot_input <- reactive({
     plot_input(data_input(),"EMPLOYER_NAME", "YEAR",reactive_inputs$metric, filter = TRUE, Ntop = reactive_inputs$Ntop)
   })

   # Employers data subset
   output$employertable <- renderDataTable({
     employer_plot_input()
   }, options = list(lengthMenu = c(10, 20,50), pageLength = 10)
   )

   # Employer Plot
   output$employer <- renderPlot({
     plot_output(employer_plot_input(),"EMPLOYER_NAME", "YEAR",reactive_inputs$metric, "EMPLOYER",
                 metric_lab_hash[[reactive_inputs$metric]])
   })

   # Map Output
   # plotting map for input metric
   # Map pinpoints to top "Ntop" worksite cities based on the input metric
   output$map <- renderPlot({
     map_gen(data_input(),reactive_inputs$metric,USA, Ntop = reactive_inputs$Ntop)
   })

   output$map_table <- renderDataTable({
     data_input() %>%
       mutate(certified =ifelse(CASE_STATUS == "CERTIFIED",1,0)) %>%
       group_by(WORKSITE) %>%
       summarise(TotalApps = n(),CertiApps = sum(certified), Wage = median(PREVAILING_WAGE))
   }, options = list(lengthMenu = c(10, 20,50), pageLength = 10))
   
   observeEvent(input$resetAll, {
     reset("inputs")
   })
   
   # session$onSessionEnded(function() {
   #   q()
   # })
   
})
```


```{r}

###### ui.r ######
library(shiny)
library(shinythemes)
library(shinyjs)

# List of choices for States input
# Entire USA or particular state
states = toupper(c("usa","alaska","alabama","arkansas","arizona","california","colorado",
  "connecticut","district of columbia","delaware","florida","georgia",
  "hawaii","iowa","idaho","illinois","indiana","kansas","kentucky",
  "louisiana","massachusetts","maryland","maine","michigan","minnesota",
  "missouri","mississippi","montana","north carolina","north dakota",
  "nebraska","new hampshire","new jersey","new mexico","nevada",
  "new york","ohio","oklahoma","oregon","pennsylvania","puerto rico",
  "rhode island","south carolina","south dakota","tennessee","texas",
  "utah","virginia","vermont","washington","wisconsin",
  "west virginia","wyoming"))
state_list <- as.list(states)
names(state_list) <- states

# Define UI for application that draws a histogram
shinyUI(
  
  fluidPage(
      
  useShinyjs(),  
  #shinythemes::themeSelector(),  
  theme = shinythemes::shinytheme("slate"),
  
  # Application title
  titlePanel("H-1B Visa Petitions Data Exploration"),

  # Sidebar with a slider input for number of bins 
  sidebarLayout(
    sidebarPanel(
      
      # CSS style for loading message whenever
      # Shiny is busy
      tags$head(tags$style(type="text/css", "
             #loadmessage {
                           position: fixed;
                           top: 0px;
                           left: 0px;
                           width: 100%;
                           padding: 5px 0px 5px 0px;
                           text-align: center;
                           font-weight: bold;
                           font-size: 100%;
                           color: #000000;
                           background-color: #CCFF66;
                           z-index: 105;
                           }
                           ")),
      

      div(
      
         id ="inputs",  
       
         # Compute button triggers server to update the outputs
         p(actionButton("resetAll", "Reset All Inputs"),
           actionButton("compute","Compute!", icon = icon("bar-chart-o"))),
         
         # Year range determines the period for data analysis
         sliderInput("year",
                     h3("Year"),
                     min = 2011,
                     max = 2016,
                     value = c(2011,2016),
                     ticks= FALSE),
         
         br(),

         h3("Job Type"),
         h6("Type up to three job type inputs. If no match found in records for all inputs, all Job Titles will be used."),
         
         div(
           id = "job_type",
           
           # Default inputs selected from my personal interest
           textInput("job_type_1", "Job Type 1","Data Scientist"),
           textInput("job_type_2", "Job Type 2","Data Engineer"),
           textInput("job_type_3", "Job Type 3", "Machine Learning")
         ),
         
         # Entire USA or a particular state in USA
         selectInput("location",
                     h3("Location"),
                     choices = state_list),
         
         h3("Employer Name"),
         h6("Type up to three Employer inputs for e.g., Google, Amazon etc. If no match found in records for all inputs, all Employers will be used."),
         div(
           id = "employer",
           textInput("employer_1", "Employer 1",""),
           textInput("employer_2", "Employer 2",""),
           textInput("employer_3", "Employer 3", "")
         ),
         

         selectInput("metric",
                     h3("Metric"),
                     choices = list("Total Visa Applications" = "TotalApps",
                                    "Wage" = "Wage",
                                    "Certified Visa Applications" = "CertiApps"
                                   )
         ),
         
         # No. of categories to be compared in each plot including the map plot
         sliderInput("Ntop",
                     h3("Plot Categories"),
                     min = 3,
                     max = 15,
                     value = 3)
         
       ),
      conditionalPanel(condition="$('html').hasClass('shiny-busy')",
                       tags$div("Loading...",id="loadmessage"))
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
      tabsetPanel(
        
        tabPanel("About",

                 tags$img(src = "http://fm.cnbc.com/applications/cnbc.com/resources/img/editorial/2014/02/28/101456986-184650923.530x298.jpg?v=1393621130",
                          alt = "H-1B Visa", align = "middle",width = "600px", height = "250px"),

                 br(),

                 br(),


                 tags$ul(
                   tags$li(tags$div("Year:", style="color:#5DADE2"), "Slider input of time period. When a single value is chosen, only that year is considered for data analysis."),
                   tags$li(tags$div("Job Type: ", style="color:#5DADE2"), "Default inputs are Data Scientist, Data Engineer and Machine Learning.
                           These are selected based on my personal interest. Explore different job titles for e.g. Product Manager, Hardware Engineer.
                           Type up to three job type inputs in the flexible text input. I avoided a drop-down menu as there are thousands of
                           unique Job Titles in the dataset. If no match found in records for all the inputs, all Job Titles in the data subset based on other inputs
                           will be used."),
                   tags$li(tags$div("Location:", style="color:#5DADE2"), "The granularity of the location parameter is State with the default option being the whole of United States"),
                   tags$li(tags$div("Employer Name:", style="color:#5DADE2"), "The default inputs are left blank as that might be the most common use case. Explore data for specific employers for e.g., Google, Amazon etc.
                           Pretty much similar in action to Job Type input."),
                   tags$li(tags$div("Metric:", style="color:#5DADE2"), "The three input metric choices are Total number of H-1B Visa applications, Certified number of Visa 
                           Applications and median annual Wage. Certified applications are filed with USCIS for H-1B approval. For more details, read this", tags$a(href="https://www.kaggle.com/nsharan/h-1b-visa/discussion/30691","discussion on Kaggle.", target= "_blank")),
                   tags$li(tags$div("Plot Categories:", style="color:#5DADE2"), "Additional control parameter for upper limit on the number of categories
                           to be used for data visualization.")
                 )

               
        ),

        tabPanel("Map",
                 plotOutput("map"),
                 br(),
                 dataTableOutput("map_table"))

        
      )
       
    )
  )
))

```
Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



